The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-10-23 borel-regularity.tex
Remove redundant definition of algebraic convolution
The previous definition already works for any translation coordinate.

\begin{old}
Similarly, we can extend the definition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
\frac{\zeta_\alpha^m}{m!} \ast_{\zeta_\alpha} \frac{\zeta_\alpha^n}{n!} \defeq \frac{\zeta_\alpha^{m+n+1}}{(m+n+1)!} \,.
Then, the unit for $\ast_{\zeta_\alpha}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha} \frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
\end{old}
We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$. The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
\[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}.\]
    We assume $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n}$. Then,
\borel_\zeta(\series{\Phi}\series{\Psi})&=\borel_\zeta\left(\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}z^{-n}\right)\\
&=a_0b_0\delta +\sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n-1}}{(n-1)!}\\
&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast_\zeta\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
&=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.
Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$. %We can further generalize this result to transseries: 
% \begin{prop}
%     The Borel transform $\borel_\zeta$ induces an algebra homomorphism 
%     \[\borel_\zeta\colon e^{-\alpha z}\C\llbracket z^{-1}\rrbracket\to \C\delta_\alpha+\C\llbracket\zeta_\alpha\rrbracket\]
%     where $\delta_\alpha:=\borel_{\zeta}e^{-z\alpha}$. 
% \end{prop}
% \begin{proof}
% Let $\series{\Phi}=e^{-\alpha z}\sum_{n=0}^\infty a_n z^{-n}\,, \series{\Psi}=e^{-\alpha z}\sum_{n=0}^\infty b_nz^{-n}\in e^{-\alpha z}\C\llbracket z^{-1}\rrbracket$. 
% %     \begin{align*}
% %         \borel_\zeta\series{\Phi}\series{\Psi}&=
% %     \end{align*}
% \end{proof}
If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, respectively, as defined in Definition~\ref{def:convolution}. We will discuss it in Section~\ref{sec:Borel-gevrey}.
\subsection{Bridging the gap between formal and analytic objects}\label{sec:bridging}
\subsubsection{Formal to analytic}\label{sec:Borel-gevrey}
If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge. These series, called {\em $1$-Gevrey} series, form a subspace $\C \llbracket z^{-1} \rrbracket_1$ within $\C \llbracket z^{-1} \rrbracket$. They are characterized by the factorial growth of their coefficients.
\begin{definition}
A series
\[ \sum_{n \ge -1} a_n z^{-n-1} \]
is {\em $1$-Gevrey} if there is some $A > 0$ with $|a_n| \lesssim A^n n!$ over all $n \ge 0$.
\begin{prop}\label{prop:gevrey_to_convergent}
A series
\[ \series{\Phi} = \sum_{n \ge -1} a_n z^{-n-1} \]
is $1$-Gevrey if and only if its Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$ is convergent.
From the expression
\[ \series{\phi} = a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}, \]
we see that $\series{\phi}$ converges if and only if there is some $A > 0$ with $|a_n / n!| \lesssim A^n$ over all $n \ge 0$. The constant $A$ is the radius of convergence of $\series{\phi}$.

>>>>

We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
\begin{prop}
Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$. The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
\[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}.\]
\end{prop}
\begin{proof}
    We assume $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n}$. Then,
    \begin{align*}
\borel_\zeta(\series{\Phi}\series{\Psi})&=\borel_\zeta\left(\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}z^{-n}\right)\\
&=a_0b_0\delta +\sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n-1}}{(n-1)!}\\
&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast_\zeta\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
&=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.
\end{align*}
\end{proof}
Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$. %We can further generalize this result to transseries: 
% \begin{prop}
%     The Borel transform $\borel_\zeta$ induces an algebra homomorphism 
%     \[\borel_\zeta\colon e^{-\alpha z}\C\llbracket z^{-1}\rrbracket\to \C\delta_\alpha+\C\llbracket\zeta_\alpha\rrbracket\]
%     where $\delta_\alpha:=\borel_{\zeta}e^{-z\alpha}$. 
% \end{prop}
% \begin{proof}
% Let $\series{\Phi}=e^{-\alpha z}\sum_{n=0}^\infty a_n z^{-n}\,, \series{\Psi}=e^{-\alpha z}\sum_{n=0}^\infty b_nz^{-n}\in e^{-\alpha z}\C\llbracket z^{-1}\rrbracket$. 
% %     \begin{align*}
% %         \borel_\zeta\series{\Phi}\series{\Psi}&=
% %     \end{align*}
% \end{proof}
\begin{remark}
If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, respectively, as defined in Definition~\ref{def:convolution}. We will discuss it in Section~\ref{sec:Borel-gevrey}.
\end{remark}
%
\subsection{Bridging the gap between formal and analytic objects}\label{sec:bridging}
%
%
\subsubsection{Formal to analytic}\label{sec:Borel-gevrey}
%
If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge. These series, called {\em $1$-Gevrey} series, form a subspace $\C \llbracket z^{-1} \rrbracket_1$ within $\C \llbracket z^{-1} \rrbracket$. They are characterized by the factorial growth of their coefficients.
\begin{definition}
A series
\[ \sum_{n \ge -1} a_n z^{-n-1} \]
is {\em $1$-Gevrey} if there is some $A > 0$ with $|a_n| \lesssim A^n n!$ over all $n \ge 0$.
\end{definition}
\begin{prop}\label{prop:gevrey_to_convergent}
A series
\[ \series{\Phi} = \sum_{n \ge -1} a_n z^{-n-1} \]
is $1$-Gevrey if and only if its Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$ is convergent.
\end{prop}
\begin{proof}
From the expression
\[ \series{\phi} = a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}, \]
we see that $\series{\phi}$ converges if and only if there is some $A > 0$ with $|a_n / n!| \lesssim A^n$ over all $n \ge 0$. The constant $A$ is the radius of convergence of $\series{\phi}$.
\end{proof}
